Title

### 2023-04-03 Cosas-Escritas-Antes.tex
Pequeña corrección
Plos one

Therfore, an OPR circuit can be transformed in a way that the rotation is around $\sigma_3$ and applied on the last qubit 
(possibly controlled by other qubits), 
so that it has the form \ref{fig: OPR general-A}. $\blacksquare$ \\ \\

@@

After $B$ creates this state, we need to apply the rotation to the result. 
This rotation will only be applied for those states on the first sum (since the fulfill the control conditions)
and not to the others. Therefore, we apply the gate to the last qubit of these states, 
remembering that $R_z(2s)$ acts by just adding a phase $e^{-is}$ to the $|0\rangle$ state
and a phase $e^{is}$ to the $|1\rangle$ state, and the result is:
\begin{eqnarray}
& \fl e^{-is} \sum_{k \in Ctrl} B_{2k,j} |k\rangle |0\rangle + e^{is} \sum_{k \in Ctrl} B_{2k+1,j} |k\rangle |1 \rangle + \sum_{k \not\in Ctrl} \left( B_{2k,j} |k\rangle |0\rangle + B_{2k+1} |k\rangle |j \rangle \right)\\
& \qquad := e^{-is} \vec{b'}_j + e^{is} \vec{a'}_j + \vec{c'}_j,
\end{eqnarray}
where $\vec{a'} = \sum_{k \in Ctrl} B_{2k,j}|k\rangle|0\rangle \;,\; \vec{b'}_j = \sum_{k \in Ctrl} B_{2k+1,j} |k\rangle |1 \rangle \;,\; \vec{c'}_j =\sum_{k \not\in Ctrl} \left( B_{2k,j} |k\rangle |0\rangle + B_{2k+1} |k\rangle |j \rangle \right) := e^{-is} \vec{b'}_j + e^{is} \vec{a'}_j + \vec{c'}_j$.
 These vectors are clearly orthogonal because they are each linear combinations of different orthogonal states of the computational basis. 
Moreover, they satisfy $|\vec{a'}_j|^2 + |\vec{b'}_j|^2 + |\vec{c'}_j|^2 = 1$ because this quantity is the norm of the $j-$th column of $B$.

@@

\begin{figure}[h!]
\centering
\includegraphics[width=0.45\textwidth]{fidelidad-puntos.png}\\
\caption{Fidelity of one qubit channels using Qiskit's ibmq-lima.}
\end{figure}

@@

\textbf{Constructing the 
Circuit:}  Given that $H$ has the form given in the theorem,
then $e^{iHt}$ can be diagonalized as $D = diag(e^{i\lambda_0 t}, \cdots , e^{i\lambda_{2^n-1}t})$,
where $2^j$ of the entries are $e^{i\lambda t}$, another $2^j$ are $e^{-i\lambda t}$ 
and the rest are $1$. 
Given a value of $j$, we construct a rotation $R_{\sigma_3}(2\lambda t)$ on the last qubit and with $n-1-j$ control qubits 
(whichever we choose, as long as they are $n-1-j$).
Therefore, the matrix representing this rotation is diagonal with $2^j$
entries being $e^{i\lambda t}$, another $2^j$ being $e^{-i\lambda t}$ and the rest being $1$.
This matrix can then be multiplied by matrices that don't depend on $t$
such that the eigenvalues are reordered and we get the matrix $D$.
That it, we can get matrix $D$ using only one rotation that depends on $t$. 
Then, because $U = Q^{-1} D Q$, we can add matrices $Q^{-1}$ and $Q$ to the circuit
to obtain the complete OPR circuit of $U$. $\blacksquare$ \\ \\

>>>>

Therfore, an OPR circuit can be transformed in a way that the rotation is around $\sigma_3$ and applied on the last qubit 
(possibly controlled by other qubits), 
so that it has the form \ref{fig: OPR general-A}. $\blacksquare$ \\

@@

After $B$ creates this state, we need to apply the rotation to the result. 
This rotation will only be applied for those states on the first sum (since the fulfill the control conditions)
and not to the others. Therefore, we apply the gate to the last qubit of these states, 
remembering that $R_z(2s)$ acts by just adding a phase $e^{-is}$ to the $|0\rangle$ state
and a phase $e^{is}$ to the $|1\rangle$ state, and the result is:
\begin{eqnarray}
& e^{-is} \sum_{k \in Ctrl} B_{2k,j} |k\rangle |0\rangle + e^{is} \sum_{k \in Ctrl} B_{2k+1,j} |k\rangle |1 \rangle + \sum_{k \not\in Ctrl} \left( B_{2k,j} |k\rangle |0\rangle + B_{2k+1} |k\rangle |j \rangle \right)\\
& \qquad := e^{-is} \vec{b'}_j + e^{is} \vec{a'}_j + \vec{c'}_j,
\end{eqnarray}
where $\vec{a'} = \sum_{k \in Ctrl} B_{2k,j}|k\rangle|0\rangle \;,\; \vec{b'}_j = \sum_{k \in Ctrl} B_{2k+1,j} |k\rangle |1 \rangle \;,\; \vec{c'}_j =\sum_{k \not\in Ctrl} \left( B_{2k,j} |k\rangle |0\rangle + B_{2k+1} |k\rangle |j \rangle \right) := e^{-is} \vec{b'}_j + e^{is} \vec{a'}_j + \vec{c'}_j$.
 These vectors are clearly orthogonal because they are each linear combinations of different orthogonal states of the computational basis. 
Moreover, they satisfy $|\vec{a'}_j|^2 + |\vec{b'}_j|^2 + |\vec{c'}_j|^2 = 1$ because this quantity is the norm of the $j-$th column of $B$.

@@

\begin{figure}[h!]
\centering
\includegraphics[width=0.45\textwidth]{fidelity-points.png}\\
\caption{Fidelity of one qubit channels using Qiskit's ibmq-lima.}
\end{figure}

@@

\textbf{Constructing the 
Circuit:}  Given that $H$ has the form given in the theorem,
then $e^{iHt}$ can be diagonalized as $D = diag(e^{i\lambda_0 t}, \cdots , e^{i\lambda_{2^n-1}t})$,
where $2^j$ of the entries are $e^{i\lambda t}$, another $2^j$ are $e^{-i\lambda t}$ 
and the rest are $1$. 
Given a value of $j$, we construct a rotation $R_{\sigma_3}(2\lambda t)$ on the last qubit and with $n-1-j$ control qubits 
(whichever we choose, as long as they are $n-1-j$).
Therefore, the matrix representing this rotation is diagonal with $2^j$
entries being $e^{i\lambda t}$, another $2^j$ being $e^{-i\lambda t}$ and the rest being $1$.
This matrix can then be multiplied by matrices that don't depend on $t$
such that the eigenvalues are reordered and we get the matrix $D$.
That it, we can get matrix $D$ using only one rotation that depends on $t$. 
Then, because $U = Q^{-1} D Q$, we can add matrices $Q^{-1}$ and $Q$ to the circuit
to obtain the complete OPR circuit of $U$. $\blacksquare$ \\
